Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-12-03 paper/sheaf_lics.tex
some corrections

\begin{defi}
  Let $E$ be a type, and $\chi:E \to \Type_n$. The subobject $\iota :
  A \to E$ of $E$
  classified by $\chi$ is {\em dense} in $E$ when its $\modal_n$-closure
  is equivalent to $\chi_E$, \ie
  %
  $$\prod_{e:E}~ \left(\sum_{e':E} e=e'\right) \simeq \modal_n
  (\chi~e).$$
  % 
  % and moreover, for any $x:A$, the following diagram 
  % commutes, 
  % $$\xymatrix{
  %   \sum_{e':A} x = e' \ar@{=}[r] \ar[d]_{\iota'} & (\chi \ x)
  %   \ar[d]^{\eta_{(\chi \ x)}}\\
  %   \sum_{e':E} x = e' \ar@{=}[r] & \modal_n (\chi \ x)
  % }$$
  % where $\iota': x \mapsto (\iota (\pi_1 x) ; \pi_2 x)$.
\end{defi}

@@

To show that $\separated$ is a modality, it remains to show point
{\it (v)} of the definition.
%
Let $A:\Type_{n+1}$ be a sheaf and $B:A \to \Type_{n+1}$ be a sheaf
family. We want to show that $\sum_{x:A} (Bx)$ is separated. Let $E$
be a type, and $\sum_{e:E} (\chi\,e)$ a dense subobject of E.

Let $f,g$ be two maps from $\sum_{e:E} (\chi\,e)$ to $\sum_{x:A}
(Bx)$, equal when precomposed with $\pi_1$.
$$\xymatrix @R=4em @C=4em{
  \sum_{e:E} (\chi\, e) \ar@<-2pt>[r]_{g\circ\pi_1} \ar@<2pt>[r]^{f\circ \pi_1} \ar[d]_{\mathrm{dense}}& \sum_{x :A} (Bx) \\
  E \ar@<-2pt>[ru]_{g} \ar@<2pt>[ru]^{f}&
}$$
We can restrict the previous diagram to 
$$\xymatrix @R=4em @C=5em{
  \sum_{e:E} (\chi\, e) \ar@<-2pt>[r]_{\pi_1\circ g\circ\pi_1} \ar@<2pt>[r]^{\pi_1\circ f\circ \pi_1} \ar[d]_{\mathrm{dense}}& \sum_{x :A} (Bx) \\
  E \ar@<-2pt>[ru]_{\pi_1\circ g} \ar@<2pt>[ru]^{\pi_1\circ f}&
}$$
and as $A$ is separated, $\pi_1\circ f = \pi_2 \circ g$.
For the second components, let $x:E$. Notice that for any $x:E$,
$\sum_{y:E} x = y$ has a dense subobject, $\sum_{y:\sum_{e:E} (\chi\,
  e)} x=y_1$:

>>>>

\begin{defi}
  Let $E$ be a type, and $\chi:E \to \Type_n$. The $n$-subobject $\iota :
  A \to E$ of $E$
  classified by $\chi$ is {\em dense} in $E$ when its $\modal_n$-closure
  is equivalent to $\chi_E$, \ie
  %
  $$\prod_{e:E}~ \left(\sum_{e':E} e=e'\right) \simeq \modal_n
  (\chi~e).$$
  % 
  % and moreover, for any $x:A$, the following diagram 
  % commutes, 
  % $$\xymatrix{
  %   \sum_{e':A} x = e' \ar@{=}[r] \ar[d]_{\iota'} & (\chi \ x)
  %   \ar[d]^{\eta_{(\chi \ x)}}\\
  %   \sum_{e':E} x = e' \ar@{=}[r] & \modal_n (\chi \ x)
  % }$$
  % where $\iota': x \mapsto (\iota (\pi_1 x) ; \pi_2 x)$.
\end{defi}

@@

To show that $\separated$ is a modality, it remains to show point
{\it (v)} of the definition.
%
Let $A:\Type_{n+1}$ be a sheaf and $B:A \to \Type_{n+1}$ be a sheaf
family. We want to show that $\sum_{x:A} (Bx)$ is separated. Let $E$
be a type, and $\sum_{e:E} (\chi\,e)$ a dense $n$-subobject of E.

Let $f,g$ be two maps from $\sum_{e:E} (\chi\,e)$ to $\sum_{x:A}
(Bx)$, equal when precomposed with $\pi_1$.
$$\xymatrix @R=4em @C=4em{
  \sum_{e:E} (\chi\, e) \ar@<-2pt>[r]_{g\circ\pi_1} \ar@<2pt>[r]^{f\circ \pi_1} \ar[d]_{\mathrm{dense}}& \sum_{x :A} (Bx) \\
  E \ar@<-2pt>[ru]_{g} \ar@<2pt>[ru]^{f}&
}$$
We can restrict the previous diagram to 
$$\xymatrix @R=4em @C=5em{
  \sum_{e:E} (\chi\, e) \ar@<-2pt>[r]_{\pi_1\circ g\circ\pi_1} \ar@<2pt>[r]^{\pi_1\circ f\circ \pi_1} \ar[d]_{\mathrm{dense}}& \sum_{x :A} (Bx) \\
  E \ar@<-2pt>[ru]_{\pi_1\circ g} \ar@<2pt>[ru]^{\pi_1\circ f}&
}$$
and as $A$ is separated, $\pi_1\circ f = \pi_2 \circ g$.
For the second components, let $x:E$. Notice that for any $x:E$,
$\sum_{y:E} x = y$ has a dense $n$-subobject, $\sum_{y:\sum_{e:E} (\chi\,
  e)} x=y_1$:
